A Comparison of Graph Processing Systems

### 2020-09-18 documentation/paper/sections/overview/gemini.tex

The real bottleneck of distributed systems is not the communication itself, but the extra instructions, as well as memory references and a lower usage of multiple cores compared to the shared memory counterparts.
The main reasons for this are (1) the use of hash maps to convert vertex IDs between local and global states, (2) the maintenance of vertex replicas, (3) the communication-bound apply phase in the GAS abstraction, and (4) the lack of dynamic scheduling \cite{Gemini}.
Gemini tries to work around all the problems mentioned above, by implemening a message-based system from scratch and getting rid of the extra mapping layer between shared-memory computation and communication.
Therefore Ligra's push-pull computation model was adopted and applied to the distributed computation.
Furthermore a chunk-based partitioning scheme was implemented, which allows to partition a graph without a large overhead.
Gemini also implements a co-scheduling mechanism to connect the computation and inter-node communication.

>>>>

The real bottleneck of distributed systems is not the communication itself, but the extra instructions, as well as memory references and a lower usage of multiple cores compared to the shared memory counterparts.
There are four main reasons for this.
The first reason is the use of hash maps to convert the vertex IDs between the global and the local state.
The second reason is the maintenance of vertex replicas on the different systems.
Another reason is the communication-bound apply phase in GAS abstraction.
And the last reason is the lack of dynamic scheduling.

Gemini tries to work around all the problems mentioned above, by implemening a message-based system from scratch and getting rid of the extra mapping layer between shared-memory computation and communication.
Therefore Ligra's push-pull computation model was adopted and applied to the distributed computation.
Furthermore a chunk-based partitioning scheme was implemented, which allows to partition a graph without a large overhead.
Gemini also implements a co-scheduling mechanism to connect the computation and inter-node communication.
